P versus NP

### 2019-12-26 doc/manuscript.tex
Improving the doc

\begin{proof}
Since the polynomial time reduction in Theorem \ref{completeness} could be easily transformed in a logarithmic space reduction, then the $\textit{NP--complete}$ problem in Theorem \ref{neg-implication}, that would be $MAX\oplus2SAT$, is necessarily in $NL$ and thus all the problems in $NP$ when $L \neq NL$, because of the Cook's Theorem can also be transformed in a logarithmic space reduction \cite{GJ79}. For the same reason, the $\textit{coNP--complete}$ problem in Theorem \ref{pos-implication}, that would be $3UNSAT$, is necessarily in $coNL$ and thus all the problems in $coNP$ when $L = NL$. Since we have either $L \neq NL$ or $L = NL$ is true, then the complexity class $NL$ is equal to $NP$.
\end{proof}

@@

We also prove that $NL = NP$. There are several important consequences from this result, but we will only mention one of the principal outcomes, that is the Theorem Buhrman-Fortnow-van Melkebeek-Torenvliet \cite{BU00}. A set $A$ is auto-reducible if there exists an oracle polynomial time Turing machine $M$ such that $L(M^{A}) = A$ with the restriction that for all $x$, $M^{A}(x)$ does not query whether $x$ is in $A$ \cite{BU00}. When $NL = NP$, Buhrman, Fortnow, van Melkebeek and Torenvliet created a series of constructions to get an $A$ such that $A$ is in $EXPSPACE$, $A$ is Turing-hard for $EXPSPACE$ and $A$ $``$diagonalizes$"$ against all possible auto-reductions \cite{BU00}.

>>>>

\begin{proof}
Since the polynomial time reduction in Theorem \ref{completeness} could be easily transformed in a logarithmic space reduction, then the $\textit{NP--complete}$ problem in Theorem \ref{neg-implication}, that would be $MAX\oplus2SAT$, is necessarily in $NL$ and thus all the problems in $NP$ when $L \neq NL$, because of the Cook's Theorem can also be transformed in a logarithmic space reduction \cite{GJ79}. Certainly, every $NP$ problem could be logarithmic space reduced to $SAT$ by the Cook's Theorem algorithm and $SAT$ can be indeed logarithmic space reduced to $\textit{NAE 3SAT}$ \cite{GJ79}. For the same reason, the $\textit{coNP--complete}$ problem in Theorem \ref{pos-implication}, that would be $3UNSAT$, is necessarily in $coNL$ and thus all the problems in $coNP$ when $L = NL$, since the problem $UNSAT$ can be actually logarithmic space reduced to $3UNSAT$ \cite{GJ79}. Since we have either $L \neq NL$ or $L = NL$ is true, then the complexity class $NL$ is equal to $NP$.
\end{proof}

@@

We also prove that $NL = NP$. There are several important consequences from this result, but we will only mention one of the principal outcomes, that would be the application of Theorem Buhrman-Fortnow-van Melkebeek-Torenvliet when $NL = NP$ \cite{BU00}.
